---
title: "US Population Stats"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(knitr)
require(XLConnect)
library(DT)
library(rpivotTable)
library(ggplot2)
library(plotly)
library(dplyr)
library(openintro)
library(highcharter)
library(ggvis)
```

```{r global, include=FALSE}
library(MASS)
data(state)
#head(state.x77)
data <- as.data.frame(state.x77)
data$state <- row.names(state.x77)
data$statecode <- state.abb
```
```{r}
mycolors <- c("blue","green","red","orange")
```

Main Page
======================================

Row
--------------------------------------

### Overall Income in US (in billions)

```{r}
valueBox(sum(data$Income),
         icon = "fa-user")
```

### **Life Expectancy Rate**

```{r}
gauge(round(mean(data$`Life Exp`),
            digits = 2),
            min = 0,
            max = 100,
            gaugeSectors(success = c(60,100),
                         warning = c(30,60),
                         danger = c(0,30),
                         colors = c('green','yellow','red')))
```

### Total Population in Massachusetts

```{r}
valueBox(sum(data['Massachusetts',]$Population))
```

### Total Population in Florida

```{r}
valueBox(sum(data['Florida',]$Population))
```

### Total Population in Texas

```{r}
valueBox(sum(data['Texas',]$Population))
```

Row
----------------------------

### Area By State

```{r}
p1 <- data %>% group_by(state) %>% summarise(Area = sum(Area))%>% plot_ly(x = ~state,
        y = ~Area,
        color = rainbow(50),
        type = 'bar') %>% layout(xaxis=list(title="Populations by State"),yaxis= list(title = 'Area in sq.ft'))
p1
```

### Scatter Plot of  Population vs Area

```{r}
p4 <- plot_ly(data, x=~Population) %>% 
  add_markers(y=~Area,
              text =~paste("State:",state),
              showlegend = F) %>% 
  add_lines(y =~fitted(loess(Population~Area)),
            name = "Loess Smoother",
            color = I("#FFC125"),
            showlegend = T,
            line = list(width =5)) %>% 
  layout(xaxis = list(title ="Population"),
         yaxis = list(title = "Area"))
p4
```

State wise Stats
============================================

### State wise Illiteracy

```{r}
p3 <- plot_ly(data,
              x=~state,
              y=~Illiteracy,
              text = paste("State:",data$state,
                           "Illiteracy:",data$Illiteracy),
              type = "bar") %>% 
  layout(xaxis = list(title = "State"),
         yaxis = list(title = "Illiteracy"))
p3
```

### Top Populated States

```{r}
p2 <- data %>% group_by(state) %>% 
  summarise(Poulation = sum(Population,na.rm = T)) %>% 
  filter(Poulation>10000) %>% 
  plot_ly(labels =~state,
          values =~Poulation,
          marker = list(colors = mycolors)) %>%
  add_pie(hole = 0.3)
p2
```

Map
==========================================

### Map 

```{r}
#abbr
s <- data %>% 
  group_by(state) %>% 
  summarise(Income = sum(Income,na.rm = T))

highchart() %>% 
  hc_title(text = "Income for each State") %>% 
  hc_subtitle(text= "Source : MASS Data") %>%
  hc_add_series_map(usgeojson,s,
                    name = "state",
                    value = "Income",
                    joinBy = c("woename","state")) %>% 
  hc_mapNavigation(enabled =T)
```

Data Table 
========================

```{r}
datatable(data,
          caption = "US Population Income Illiteracy Data",
          rownames = T,
          filter = "top",
          extensions = 'Buttons',
      options = list(
        pageLength = 25,
        dom = 'Blfrtip',
        buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
      ))
```

Pivot Table
=========================================

```{r}
rpivotTable(data,
            aggregatorName = "Sum",
            cols= "",
            rows = "state",
            vals = "Income",
            rendererName = "Bar Chart")
```

Summary {data-orientation=columns} 
===========================================

Column 
-----------------------------------

### High Population

```{r}
valueBox(max(data$Population),
         icon = "fa-user" )
```

### Average Income
```{r}
valueBox(round(mean(data$Income),
               digits = 2),
         icon = "fa-area-chart")
```

### Average Life Expectancy

```{r}
valueBox(round(mean(data$`Life Exp`), digits = 2),
         icon = "fa-area-chart")
```

Column
---------------------------

Report

* This is a report on `r length(data$state)` States in US.

* Largest among the States is `r data$state[data$Area == max(data$Area)]` with an Area of `r max(data$Area)` sq miles.

* The average murder rate was `r mean(data$Murder)`.

This report was generated on `r format(Sys.Date(), format = "%B %d, %Y")`.

Reactive Part
========================================

Column {.sidebar}
-----------------------------------------------------------------------
  

```{r}
selectInput(inputId = "p_state", label = strong("Select a State"),
                                choices =  unique(data$state),selected = "California")

            
```


```{r}
textInput("Name", "Enter your Name", "VigneshEA")
```


Column
------------------------------------------

### Selected State Total Income

```{r}
summary_data <- reactive({
  ip <- input$p_state
  final_data <- filter(data, state == ip)
  final_data
    })


renderPrint({
  summary_data()
    })
```

Row 
--------------------------------

### User Name 

```{r}
p_name <- reactive({
Name <- input$Name
Name
})


renderText({ 
  p_name()
  })
```





About Report
========================================

Created by: Vignesh EA

Confidential: Nothing like that!






